\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-25 doc/USER_MANUAL/manual_SPECFEM3D.tex
updates SPECFEM3D configure script and manual regarding scotch installation

The SCOTCH library \citep{PeRo96}
provides efficent static mapping, graph and mesh partitioning routines. SCOTCH is a free software package developed by
Fran\c {c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}. It is more recent than METIS, actively maintained and performs better in many cases.
A recent version of its source code is provided in directory \texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}.
The path to the SCOTCH installation needs to be set with the option \texttt{-{}-with-scotch-path}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-path=/opt/scotch
\end{lyxcode}

@@

\noindent\texttt{./configure FC=xlf90\_r MPIFC=mpif90 CC=xlc\_r CFLAGS="-O3 -q64" FCFLAGS="-O3 -q64" -with-scotch-path=...}.\\

@@

Prior to compiling \texttt{decompose\_mesh\_SCOTCH}, make sure you have correctly specified the path
of the SCOTCH library with the option \texttt{-{}-with-scotch-path} of the \texttt{configure} script.
For convenience we provide the source code of SCOTCH, which is released open source under the French CeCILL-C version 1 license,
in directory ~\\
\texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}. Please refer to file INSTALL.txt in that directory to see how to compile it.
In the future you should be able to find more recent versions at  \url{http://www.labri.fr/perso/pelegrin/scotch/scotch\_en.html} .
\\

@@

\texttt{./configure FC=ifort MPIFC=mpif90 --with-scotch-path=/opt/scotch}\\

>>>>

The SCOTCH library \citep{PeRo96}
provides efficent static mapping, graph and mesh partitioning routines. SCOTCH is a free software package developed by
Fran\c {c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}. It is more recent than METIS, actively maintained and performs better in many cases.
A recent version of its source code is provided in directory \texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}.
The path to an existing SCOTCH installation can to be set with the option \texttt{-{}-with-scotch-dir}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-dir=/opt/scotch
\end{lyxcode}

@@

\noindent\texttt{./configure FC=xlf90\_r MPIFC=mpif90 CC=xlc\_r CFLAGS="-O3 -q64" FCFLAGS="-O3 -q64" -with-scotch-dir=...}.\\

@@

Prior to compiling \texttt{decompose\_mesh\_SCOTCH}, make sure you have correctly specified the path
of the SCOTCH library with the option \texttt{-{}-with-scotch-dir} of the \texttt{configure} script.
For convenience we provide the source code of SCOTCH, which is released open source under the French CeCILL-C version 1 license,
in directory ~\\
\texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}. Please refer to file INSTALL.txt in that directory to see how to compile it.
In the future you should be able to find more recent versions at  \url{http://www.labri.fr/perso/pelegrin/scotch/scotch\_en.html} .
\\

@@

\texttt{./configure FC=ifort MPIFC=mpif90 --with-scotch-dir=/opt/scotch}\\
